---
title: "In-Session Code"
output:
  html_document:
    toc: true
    number_sections: false
    toc_float:
      collapsed: false
      smooth_scroll: true
    self_contained: true
bibliography: refs.bib
biblio-style: authoryear
editor_options: 
  chunk_output_type: console
---


```{r echo = FALSE, include = TRUE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, tidy = 'styler')
```

Libraries and settings

```{r message = FALSE}
library(tidyverse)
library(rstan)
library(sbcrs)
rstan_options(auto_write = TRUE)
doParallel::registerDoParallel(cores = parallel::detectCores())
options(mc.cores = parallel::detectCores())
```

# One good, price per unit

## Utility

The consumer chooses a quantity $x$ of a single good $i$. Dropping the $i$ subscript, we know from Equation (6) in [@lee2014modeling] the utility from the good:$$
u(x_{t}) = \frac{\alpha \mathrm{e}^{\epsilon_t}}{\gamma} \log(\gamma s x_t +  1)
$$

Let's pause here to consider the structure of this utility function.

```{r}
u <- function(x, alpha, gamma, s, epsilon) {
  alpha * exp(epsilon) / gamma * log1p(gamma * s * x)
}
crossing(x = seq_len(11) - 1L, 
         alpha = round(10/log(11) * c(.25, .5, 1), 2), 
         gamma = round(c(1, 2.35526, 5.4011), 2),  
         s = round(c(1/10 *(-1 + sqrt(11)), 1, 12), 2),
         epsilon = 0) %>%
  mutate(u = u(x, alpha, gamma, s, epsilon)) %>%
  ggplot(aes(x = x, y = u, colour = factor(gamma))) +
  geom_point(alpha = .5) +
  geom_line() +
  facet_grid(alpha~s, labeller = label_both) +
  scale_x_continuous(breaks = seq_len(11) - 1L) +
  labs(colour = expression(gamma)) +
  theme_bw()
```

The parameters in this utility function serve the following purposes:

* $\alpha$ determines the marginal utility from higher  $x$ at the point $x = 0$, when $s = 1$ and $\gamma = 1$
  
```{r}
crossing(x = exp(seq(log(.01), log(.1), by = .01)),
         alpha = c(.5, 1, 2),
         gamma = 1,
         s = 1,
         epsilon = 0) %>%
  mutate(u = u(x, alpha, gamma, s, epsilon)) %>%
  ggplot(aes(x = x, y = u,  colour = factor(alpha))) +
  geom_line() +
  labs(colour = expression(alpha)) +
  theme_bw() 
```

* $\gamma$ shifts indifference curves to allow corner solutions
  
```{r}
crossing(x = seq(-1.25, 6, by = .01),
         gamma = c(.25, .5, .75)) %>%
  mutate(w = 1 - x/(2*(1+x*gamma)))  %>%
  filter(w < 3) %>%
  ggplot(aes(x = x, y = w,  colour = factor(gamma))) +
  geom_line() +
  theme_bw() +
    labs(y = 'Money',
         x = 'Consumption quantity of good i',
         colour = expression(gamma))
```

* $s$ rescales $x$ into "standard units"


The utility from any remaining budget is $$u_0(x_t) = \alpha_0(M_t-p_t x_t)$$ meaning utility is linear in money. Note that $p_t$ is the price *per unit* of $x_t$. Hence total price $p_t(x_t) = p_t x_t$, which is linear in $x_t$.

## Choices

Assume the consumer can choose any amount of $x \in \{ 0, 1, \dots\}$ to purchase. Equation (9) becomes $$
\begin{aligned}
U^*(x_t^*) &\geq \max\left\{U^*(x_t + \Delta) | x_t^* \in F\right\}_{\Delta \in \{-1, 1\}} \\
F & \equiv \left\{ x_t | M_t - p_t x_t \geq 0, x_t \in \{0, 1, \dots \} \right\}
\end{aligned}$$

In  words, this means that the highest utility attainable is at the quantity $x^*$. This quantity $x^*$ has a few restrictions:

1. It needs to be affordable, so that $p_t x_t^* \leq M_t$
2. It needs to be zero or a positive integer
3. The utility from the quantity $x^*$ cannot be less than the utility from either $x^* + 1$ or $x^* - 1$ (if those are feasible given the constrains above)
 
## Likelihood

Equation (10) is derived by substituting the utility function in (6) into Equation (9). It's simplest to start by expanding Equation (9) assuming that $x^*+1$ is feasible and $x^*$ is positive. There are two cases to consider, but we can simplify the problem by letting $x^\pm_t$ stand in for both cases. 
$$
\begin{aligned}
U(x_t) &\geq U(x^\pm_t)  \\
\frac{\alpha \mathrm{e}^{\epsilon_t}}{\gamma} \log(\gamma s x_t +  1) + \alpha_0(M_t-p_t x_t) 
  &\geq \frac{\alpha \mathrm{e}^{\epsilon_t}}{\gamma} \log(\gamma s x_t^\pm +  1) + \alpha_0(M_t-p_t x_t^\pm)  \\
\frac{\alpha \mathrm{e}^{\epsilon_t}}{\gamma} \log(\gamma s x_t +  1) - \alpha_0(p_t x_t) 
  &\geq \frac{\alpha \mathrm{e}^{\epsilon_t}}{\gamma} \log(\gamma s x_t^\pm +  1) - \alpha_0(p_t x_t^\pm) \\
\frac{\alpha \mathrm{e}^{\epsilon_t}}{\gamma} \left[ \log(\gamma s x_t +  1) - \log(\gamma s x_t^\pm +  1) \right]
  &\geq \alpha_0 p_t( x_t -  x_t^\pm)\\
\end{aligned}$$

When $x_t^\pm = x_t - 1$ then we have
$$
\begin{aligned}
\frac{\alpha \mathrm{e}^{\epsilon_t}}{\gamma} \left[ \log(\gamma s x_t +  1) - \log(\gamma s (x_t - 1) +  1) \right]
  &\geq \alpha_0 p_t\\
  \mathrm{e}^{\epsilon_t}\left[ \log\left(\frac{\gamma s x_t +  1}{\gamma s (x_t - 1)  +  1}\right) \right]
  &\geq \frac{\alpha_0 p_t \gamma }{\alpha}\\
  \mathrm{e}^{\epsilon_t}
  &\geq \frac{\alpha_0 p_t \gamma }{\alpha}\left[ \log\left(\frac{\gamma s x_t +  1}{\gamma s (x_t - 1)  +  1}\right) \right]^{-1}\\
  \epsilon_t &\geq \log\left(\frac{\alpha_0 p_t\gamma }{\alpha}\right) - \log\left[ \log\left(\frac{\gamma s x_t +  1}{\gamma s (x_t - 1)+  1}\right) \right]\equiv \widetilde{lb}_t(x_t)
\end{aligned}$$

When $x_t^\pm = x_t + 1$ then we have $$
\begin{aligned}
\frac{\alpha \mathrm{e}^{\epsilon_t}}{\gamma} \left[ \log(\gamma s x_t +  1) - \log(\gamma s (x_t + 1) +  1) \right]
  &\geq - \alpha_0 p_t\\
  \frac{\alpha \mathrm{e}^{\epsilon_t}}{\gamma} \left[  \log(\gamma s (x_t + 1) +  1) -\log(\gamma s x_t +  1)  \right]
  &\leq  \alpha_0 p_t\\
  \mathrm{e}^{\epsilon_t}\left[ \log\left(\frac{\gamma s (x_t + 1)  +  1}{\gamma s x_t +  1}\right) \right]
  &\leq \frac{\alpha_0 p_t \gamma }{\alpha}\\
  \mathrm{e}^{\epsilon_t}
  &\leq \frac{\alpha_0 p_t \gamma }{\alpha}\left[ \log\left(\frac{\gamma s (x_t + 1)  +  1}{\gamma s x_t +  1}\right) \right]^{-1}\\
  \epsilon_t
  &\leq \log\left(\frac{\alpha_0 p_t \gamma }{\alpha}\right) - \log\left[ \log\left(\frac{\gamma s (x_t + 1)  +  1}{\gamma s x_t +  1}\right) \right]\equiv \widetilde{ub}_t(x_t)
\end{aligned}$$

From the standpoint of estimation, the upper and lower bounds on $\epsilon_t$ have a  natural meaning. We assume that $x_t$ is optimal. Given that it is optimal, then $\epsilon_t$ must be less than $\widetilde{ub}_t(x_t)$. Why? Because if $\epsilon_t$ was greater than $\widetilde{ub}_t(x_t)$, then we would have observed a bigger value of $x_t$. Similarly, $\epsilon_t$ had to be greater than $\widetilde{lb}_t(x_t)$, because otherwise we would have observed a smaller $x_t$. 

The edge cases are straightforward. If the optimal $x_t = 0$ then we don't know how low $\epsilon_t$ was.  We set $lb_t(x_t) = -\infty$ in that case. And if the $x_t + 1$ violates the  budget constraint, then we don't know how big $\epsilon_t$ was. In that case, we set $ub_t(x_t) = \infty$. 

In summary, $$
\begin{aligned}
& lb_t(x_t) \leq \epsilon_t \leq ub_t(x_t) \\
lb_t(x_t) =& \begin{cases}\widetilde{lb}_t(x_t) & x_t > 0 \\
                     -\infty & x_t = 0
                     \end{cases}\\
ub_t(x_t) =& \begin{cases}\widetilde{ub}_t(x_t) & (x_t + 1) p_t \leq M_t \\
                     \infty & (x_t + 1) p_t >  M_t
                     \end{cases}
\end{aligned}$$

Given all this complexity, the likelihood is surprisingly simple. The likelihood of the observed quantity $x_t$ is the probability of the set of $\epsilon_t$'s that fall between the lower and upper bounds. Let $f(\epsilon)$ and $F(\epsilon)$ denote the pdf and cdf of $\epsilon_t$ respectively—the likelihood of $x_t$ is:
$$\begin{aligned}
\ell(x_t) & = \int^{ub_t(x_t)}_{lb_t(x_t)} f(\epsilon) d\epsilon \\
& = F(ub_t(x_t)) - F(lb_t(x_t))
\end{aligned}$$

The plot below shows the distribution of $\epsilon_t\sim N(0,\sigma^2)$, and the regions that would rationalize various values of $x_t$. The highlighted area is the total probability of $x_t = 3$ given $\gamma = 2$, $\alpha = 3$, $\alpha_0 = s = 1$, $M = 10$, and $p = 1$. Maximizing the likelihood of $x_t = 3$ implies finding parameter values that lead to the largest possible highlighted region.

```{r}
bound <- function(ux, lx = NULL, dp = 1, gamma = 2, alpha = 3, M = 10) {
  if (ux == 0)
    return (-Inf)
  if (ux * dp > M)
    return (Inf)
  if (is.null(lx))
    lx <- ux - 1
  log(dp * gamma) - log(alpha) - log(log1p(gamma * ux) - log1p(gamma * lx))
}
pd <- 
  tibble(ux = -1L + seq_len(13),
         lx = ux - 1L) %>%
  mutate(b = map_dbl(ux, ~bound(.x)),
         pb = dnorm(b),
         labx = .5*b  + .5 * lead(b),
         labx = ifelse(is.infinite(labx) & !is.infinite(b),
                       b + (b - lag(b)), labx),
         labx = ifelse(ux == 0, lead(b) - .5, labx)) %>%
  filter(ux < 11)
fd <-
  tibble(x = seq(bound(3), bound(4), by = .01),
         y  = 0) %>%
  bind_rows(tibble(x = seq(bound(4), bound(3), by = -.01),
            y = dnorm(x)))
ggplot(NULL) +
  geom_polygon(aes(x, y), fd, fill = scales::muted(
    'red', l = 50, c = 100)) +
  stat_function(aes(x = seq(-3, 3, by = .01)),
                fun = dnorm) +
  geom_segment(aes(x = b, xend = b, y = 0, yend = pb),
               pd) +
  geom_text(aes(x = labx, y = 0, label = ux), pd,
            nudge_y = -.01) +
  theme_bw() +
  labs(x = expression(epsilon), y = expression(f(epsilon)))
```


## Simulation

We'll assume $\epsilon_t\sim N(0,\sigma^2)$. We'll also set $s = 1$ and $\alpha_0 = 1$, leading to:

$$
\begin{aligned}
{lb}_t(x_t) &\equiv \begin{cases}
\log\left(\frac{p_t\gamma }{\alpha}\right) - \log\left[ \log\left(\frac{\gamma  x_t +  1}{\gamma (x_t - 1) +  1}\right) \right], & x_t > 0 \\
-\infty, & x_t = 0
\end{cases}
\\
{ub}_t(x_t) &\equiv \begin{cases}
\log\left(\frac{p_t \gamma }{\alpha}\right) - \log\left[ \log\left(\frac{\gamma  (x_t+1)  +  1}{\gamma  x_t +  1}\right) \right], & (x_t + 1) p_t \leq M_t \\
\infty, & (x_t + 1) p_t >  M_t
\end{cases}\\
\ell(x_t)&= \Phi\left(\frac{ub_t(x_t)}{\sigma}\right) - \Phi\left(\frac{lb_t(x_t)}{\sigma}\right)
\end{aligned}
$$

```{r}
gen_data <- function(seed) {
  set.seed(1e6+seed)
  
  T <- 10
  M <- rep(10, T) + sample.int(3, T, replace = TRUE) - 1L
  p <- rep(.5, T)
  
  pcer <- function(U, a) (- log(a)/U)
  sigma_rate <- pcer(1, .1)
  alpha_rate <- pcer(1, .5)
  gamma_rate <- pcer(1, .1)
  
  list(T = T, p = p, M = M, sigma_rate = sigma_rate,
       alpha_rate = alpha_rate, gamma_rate = gamma_rate)
}
gen_params <- function(seed, data) {
  set.seed(2e6+seed)
  sigma_raw <- rgamma(1, 2, rate = .5)
  alpha_raw <- rexp(1)
  gamma_raw <- rexp(1)
  list(sigma_raw = sigma_raw, alpha_raw = alpha_raw, gamma_raw = gamma_raw)
}
gen_modeled_data <- function(seed, data, params) {
  set.seed(3e6+seed)
  sigma <- params$sigma_raw / data$sigma_rate
  alpha <- params$alpha_raw / data$alpha_rate
  gamma <- 1 + params$gamma_raw / data$gamma_rate
  epsilon <- rnorm(data$T, 0, 1) * sigma
  optx <- function(alpha, sigma, gamma, epsilon_t, M_t, p_t) {
    Ux <- function(x, alpha, gamma, epsilon_t, M_t, p_t) {
      u <- alpha * exp(epsilon_t) / gamma * log1p(gamma * x) + M_t - p_t * x
      u[M_t < p_t * x] <- -Inf
      u
    }
    maxx <- floor(M_t/p_t)
    which.max(Ux(seq_len(maxx + 1) - 1, alpha, gamma, epsilon_t, M_t, p_t)) - 1L
  }
  x <- seq_len(data$T) %>%
    map_dbl(~optx(alpha, sigma, gamma, epsilon[.x], data$M[.x], data$p[.x]))
  list(x = x)
}
prior_predictive_distribution <- function(seed) {
    data <- gen_data(seed)
    params <- gen_params(seed, data)
    gen_modeled_data(seed, data, params)
}
seq_len(100) %>%
  map(~prior_predictive_distribution(.x)) %>%
  unlist() %>%
  as.vector() %>%
  tibble(x = .) %>%
  ggplot(aes(x = x)) + 
  stat_bin(bins = 21) +
  theme_bw()
```

Stan model `model1.stan`:

```{r comment = '', echo = FALSE}
read_file('model1.stan') %>% cat(sep = '\n')
```


```{r}
the_model <- stan_model('model1.stan', save_dso = TRUE)
sample_from_stan <- function(seed, data, params, modeled_data, iters) {
  modeled_data$x <- as.array(modeled_data$x)
  data$p <- as.array(data$p)
  data$M <- as.array(data$M)
  data$no_lb <- as.array(1L * (modeled_data$x == 0))
  data$no_ub <- as.array(1L * ((modeled_data$x + 1) * data$p > data$M))

  stopifnot(all(modeled_data$x * data$p <= data$M))

  data_for_stan <- c(data, modeled_data)
  sampling(the_model, data = data_for_stan, seed = seed,
           chains = 1, iter = 2 * iters, warmup = iters, 
           open_progress = FALSE, show_messages = FALSE,
           refresh = 1000)
}
```

```{r cache = TRUE}
doParallel::registerDoParallel(cores = parallel::detectCores())
sbc <- SBC$new(gen_data, gen_params, gen_modeled_data, sample_from_stan)
sbc$calibrate(512, 20)
sbc$plot()
sbc$summary()
```

# One good, not all x's are feasible, no standard price per unit

In the previous example, total price was $p_t x_t$. In practice, this is not usually the case, due for example to volume discounts. If prices instead are a function of $x_t$, then the utility from the remaining budget becomes 
$$
u_0(x_t) = \alpha_0(M - p_t(x_t))
$$

If we observe prices,  then we do not need to know the function $p_t()$ and can instead just condition on what is observed. But the possibly non-linear relationship between $x_t$ and total price means the likelihood function will need to change. 

It might also be the case that the quantity of a good might not be easily expressible as a sequence of integers. For example, some $x$'s might not be feasible. In that case, $x^\pm_t$ may not equal $x_t - 1$ or $x_t + 1$. If we always  have $x_t + c$ and $x_t - c$ in the data, then we can use the $s_t$ term  in the utility function to rescale the $x_t$'s so that they are in single integer units. But that will not typically be the case.

## Likelihood

In either of these cases, derivation of the likelihood is very similar to what we have already seen, but with a few small differences:

$$
\begin{aligned}
U(x_t) &\geq U(x^\pm_t)  \\
\frac{\alpha \mathrm{e}^{\epsilon_t}}{\gamma} \log(\gamma s x_t +  1) + \alpha_0(M_t-p_t(x_t)) 
  &\geq \frac{\alpha \mathrm{e}^{\epsilon_t}}{\gamma} \log(\gamma s x_t^\pm +  1) + \alpha_0(M_t-p_t(x_t^\pm))  \\
\frac{\alpha \mathrm{e}^{\epsilon_t}}{\gamma} \log(\gamma s x_t +  1) - \alpha_0(p_t(x_t))
  &\geq \frac{\alpha \mathrm{e}^{\epsilon_t}}{\gamma} \log(\gamma s x_t^\pm +  1) - \alpha_0(p_t(x_t^\pm)) \\
\frac{\alpha \mathrm{e}^{\epsilon_t}}{\gamma} \left[ \log(\gamma s x_t +  1) - \log(\gamma s x_t^\pm +  1) \right]
  &\geq \alpha_0 \left[p_t(x_t) -  p_t(x_t^\pm))\right]\\
\end{aligned}$$

We'll work through the case when $x_t^\pm \equiv x_t^- < x_t$, the case for $x_t^\pm \equiv x_t^+ > x_t$ is similar.

First, define $p_t \equiv p_t(x_t)$ and $p_t^- \equiv p_t(x_t^-)$. Note that it must be the case that $p_t^- < p_t$, otherwise we cannot rationalize the consumers' choice of $x_t$. 

$$
\begin{aligned}
\frac{\alpha \mathrm{e}^{\epsilon_t}}{\gamma} \left[ \log(\gamma s x_t +  1) - \log(\gamma s x_t^- +  1) \right]
  &\geq \alpha_0 (p_t -  p_t^-)\\
  \mathrm{e}^{\epsilon_t}\left[ \log\left(\frac{\gamma s x_t +  1}{\gamma s x_t^-  +  1}\right) \right]
  &\geq \frac{\alpha_0 (p_t -  p_t^-) \gamma }{\alpha}\\
  \mathrm{e}^{\epsilon_t}
  &\geq \frac{\alpha_0 (p_t -  p_t^-) \gamma }{\alpha}\left[ \log\left(\frac{\gamma s x_t +  1}{\gamma s x_t^-  +  1}\right) \right]^{-1}\\
  \epsilon_t &\geq \log\left(\frac{\alpha_0 (p_t -  p_t^-)\gamma }{\alpha}\right) - \log\left[ \log\left(\frac{\gamma s x_t +  1}{\gamma s x_t^- +  1}\right) \right]\equiv \widetilde{lb}_t(x_t)
\end{aligned}$$

To estimate the likelihood, we need different data  than before. Previously, we needed only the observed units purchased, $x_t$, and  the price per unit $p_t$. Now we need information about the next highest and next lowest feasible units, $x_t^+$ and $x_t^-$, as well as their corresponding prices, $p_t^+$ and $p_t^-1$. These may or may not be available in the data, in which case it might be necessary to impute the values of the neighboring, feasible units  and prices. 

## Simulation

```{r}
gen_data <- function(seed) {
  set.seed(1e6+seed)
  
  feasible_x <- c(0, 1, 2, 3, 6, 12, 24)
  
  T <- 10
  M <- rep(10, T) + sample.int(3, T, replace = TRUE) - 1L
  p <- map(feasible_x, ~round(.x * .5  - .15* log1p(rep(.5, T)*.x), 2)) %>%
    transpose() %>%
    map(~unlist(.x))
  
  pcer <- function(U, a) (- log(a)/U)
  sigma_rate <- pcer(1, .1)
  alpha_rate <- pcer(1, .5)
  gamma_rate <- pcer(1, .1)
  
  list(T = T, p = p, M = M, sigma_rate = sigma_rate,
       alpha_rate = alpha_rate, gamma_rate = gamma_rate,
       feasible_x = feasible_x)
}
gen_params <- function(seed, data) {
  set.seed(2e6+seed)
  sigma_raw <- rgamma(1, 2, rate = .5)
  alpha_raw <- rexp(1)
  gamma_raw <- rexp(1)
  list(sigma_raw = sigma_raw, alpha_raw = alpha_raw, gamma_raw = gamma_raw)
}
gen_modeled_data <- function(seed, data, params) {
  set.seed(3e6+seed)
  sigma <- params$sigma_raw / data$sigma_rate
  alpha <- params$alpha_raw / data$alpha_rate
  gamma <- 1 + params$gamma_raw / data$gamma_rate
  epsilon <- rnorm(data$T, 0, 1) * sigma
  optx <- function(alpha, sigma, gamma, epsilon_t, M_t, p_t) {
    Ux <- function(x, alpha, gamma, epsilon_t, M_t, p_t) {
      u <- alpha * exp(epsilon_t) / gamma * log1p(gamma * x) + M_t - p_t
      u[M_t < p_t] <- -Inf
      u
    }
    data$feasible_x[
      which.max(Ux(data$feasible_x, alpha, gamma, epsilon_t, M_t, p_t))
      ]
  }
  
  x <- seq_len(data$T) %>%
    map_dbl(~optx(alpha, sigma, gamma, epsilon[.x], data$M[.x], data$p[[.x]]))
  list(x = x)
}
prior_predictive_distribution <- function(seed) {
    data <- gen_data(seed)
    params <- gen_params(seed, data)
    modeled_data <- gen_modeled_data(seed, data, params)
    modeled_data
}
seq_len(100) %>%
  map(~prior_predictive_distribution(.x)) %>%
  unlist() %>%
  as.vector() %>%
  tibble(x = .) %>%
  ggplot(aes(x = x)) + 
  stat_count() +
  theme_bw()
```

Stan model `model2.stan`:

```{r comment = '', echo = FALSE}
read_file('model2.stan') %>% cat(sep = '\n')
```


```{r}
the_model_2 <- stan_model('model2.stan', save_dso = TRUE)

sample_from_stan <- function(seed, data, params, modeled_data, iters) {
  ix <- map_dbl(modeled_data$x, ~which(.x == data$feasible_x))
  uix <- ix + 1
  uix[uix > length(data$feasible_x)] <- NA
  lix <- ix - 1
  lix[lix == 0] <- NA
  modeled_data$ux <- as.array(data$feasible_x[uix])
  modeled_data$lx <- as.array(data$feasible_x[lix])
  modeled_data$x <- as.array(modeled_data$x)
  
  data$up <- as.array(map2_dbl(data$p, uix, ~.x[.y]))
  data$lp <- as.array(map2_dbl(data$p, lix, ~.x[.y]))
  data$p <- as.array(map2_dbl(data$p, ix, ~.x[.y]))
  
  data$M <- as.array(data$M)

  data$no_lb <- as.array(1L*(is.na(modeled_data$lx)))
  data$no_ub <- as.array(1L*(is.na(modeled_data$ux) | data$up > data$M))

  modeled_data$lx[data$no_lb == 1L] <- 0
  modeled_data$ux[data$no_ub == 1L] <- 0
  data$lp[data$no_lb == 1L] <- 0
  data$up[data$no_ub == 1L] <- 0
  
  stopifnot(all(data$p <= data$M))
  
  data_for_stan <- c(data, modeled_data)
  sampling(the_model_2, data = data_for_stan, seed = seed,
           chains = 1, iter = 2 * iters, warmup = iters, 
           open_progress = FALSE, show_messages = FALSE,
           refresh = 1000)
}
```

```{r cache = TRUE}
doParallel::registerDoParallel(cores = parallel::detectCores())
sbc <- SBC$new(gen_data, gen_params, gen_modeled_data, sample_from_stan)
sbc$calibrate(512, 20, keep_stan_fit = FALSE)
sbc$plot()
sbc$summary()
```

# References
